Prevalence, ANC, ART model inference case-study

### 2022-09-08 src/prev-anc-art_process-results/prev-anc-art.Rmd
Iterate prev-anc-art forward

    **Findings**

    **Next steps**
---

@@

| Model | Report | Components |
|-------|--------| ---------- |
| 0 | [`prev-anc-art_model0`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model0) | Prevalence (no random effects) |
| 1 | [`prev-anc-art_model1`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model1) | Prevalence |
| 2 | [`prev-anc-art_model2`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model2) | Prevalence, ANC |
| 3 | [`prev-anc-art_model3`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model3) | Prevalence, ART |
| 4 | [`prev-anc-art_model4`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model4) | Prevalence, ANC, ART |

@@

| Parameter | Value |
|-----------|-------|
| $n$              | 30   |
| $m_i$            | 250  |
| $\beta_\rho$     | -2.4 |
| $\sigma_\rho$    | 0.5  |
| $m^\text{ANC}_i$ | 10^4 |
| $\beta_b$        | -0.2 |
| $\sigma_b$       | 0.1  |
| $N_i$            | 10^5 |
| $\beta_\alpha$   | 0.7 |
| $\sigma_\alpha$  | 0.35 |

@@

```{r setup, class.source = 'fold-hide'}
knitr::opts_chunk$set(
  cache = TRUE,
  autodep = TRUE,
  cache.lazy = FALSE,
  cache.comments = FALSE
)
options(scipen = 999)
cbpalette <- multi.utils::cbpalette()
library(tidyverse)
rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

@@

```{r cache=FALSE}
# draw_boxplots(model0) + labs(title = "Model 0")
# draw_boxplots(model1) + labs(title = "Model 1")
# draw_boxplots(model2) + labs(title = "Model 2")
# draw_boxplots(model3) + labs(title = "Model 3")
# draw_boxplots(model4) + labs(title = "Model 4")
```

@@

```{r fig.height=15}
# draw_scatterplots(model0) + labs(title = "Model 0")
draw_scatterplots(model1) + labs(title = "Model 1")
draw_scatterplots(model2) + labs(title = "Model 2")
draw_scatterplots(model3) + labs(title = "Model 3")
draw_scatterplots(model4) + labs(title = "Model 4")
```

@@

```{r fig.height=8}
# draw_ksplots_D(model0) + labs(title = "Model 0")
draw_ksplots_D(model1) + labs(title = "Model 1")
draw_ksplots_D(model2) + labs(title = "Model 2")
draw_ksplots_D(model3) + labs(title = "Model 3")
draw_ksplots_D(model4) + labs(title = "Model 4")
```

@@

```{r fig.height=8}
# draw_ksplots_D(model0) + labs(title = "Model 0")
# draw_ksplots_l(model1) + labs(title = "Model 1")
# draw_ksplots_l(model2) + labs(title = "Model 2")
# draw_ksplots_l(model3) + labs(title = "Model 3")
# draw_ksplots_l(model4) + labs(title = "Model 4")
```

@@

```{r}
# map(model0, "mcmc_traceplots")
map(model1, "mcmc_traceplots")
map(model2, "mcmc_traceplots")
map(model3, "mcmc_traceplots")
map(model4, "mcmc_traceplots")
```

@@

```{r}
# draw_rhatplot(model0) + labs(title = "Model 0")
draw_rhatplot(model1) + labs(title = "Model 1")
draw_rhatplot(model2) + labs(title = "Model 2")
draw_rhatplot(model3) + labs(title = "Model 3")
draw_rhatplot(model4) + labs(title = "Model 4")
```

>>>>

    **Findings** We find that, treating `tmbstan` as the gold-standard, inference from `TMB` is substantially worse than than from `aghq` .

    **Next steps** Work on presentation of document. Understand performance for different parameters. Understand cause of poor performance.
---

@@

| Model | Report | Components |
|:------|:-------|:-----------|
| 0 | [`prev-anc-art_model0`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model0) | Prevalence (no random effects) |
| 1 | [`prev-anc-art_model1`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model1) | Prevalence |
| 2 | [`prev-anc-art_model2`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model2) | Prevalence, ANC |
| 3 | [`prev-anc-art_model3`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model3) | Prevalence, ART |
| 4 | [`prev-anc-art_model4`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model4) | Prevalence, ANC, ART |

@@

| Parameter | Value |
|:----------|:------|
| $n$              | 30   |
| $m_i$            | 250  |
| $\beta_\rho$     | -2.4 |
| $\sigma_\rho$    | 0.5  |
| $m^\text{ANC}_i$ | 10^4 |
| $\beta_b$        | -0.2 |
| $\sigma_b$       | 0.1  |
| $N_i$            | 10^5 |
| $\beta_\alpha$   | 0.7 |
| $\sigma_\alpha$  | 0.35 |

@@

```{r setup, message=FALSE, class.source = 'fold-hide'}
knitr::opts_chunk$set(
  cache = TRUE,
  autodep = TRUE,
  cache.lazy = FALSE,
  cache.comments = FALSE
)
options(scipen = 999)
cbpalette <- multi.utils::cbpalette()
library(tidyverse)
rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

@@

Boxplots of the mean and standard deviation for each parameter, where each datapoint is a different simulation replicate.

```{r cache=FALSE}
params <- c("beta_prev", "log_sigma_phi_prev")

draw_boxplots(model1, params = params) + labs(title = "Model 1")
draw_boxplots(model2, params = params) + labs(title = "Model 2")
draw_boxplots(model3, params = params) + labs(title = "Model 3")
draw_boxplots(model4, params = params) + labs(title = "Model 4")
```

@@

```{r}
params <- c("beta_prev", "log_sigma_phi_prev")

draw_scatterplots(model1, params = params) + labs(title = "Model 1")
draw_scatterplots(model2, params = params) + labs(title = "Model 2")
draw_scatterplots(model3, params = params) + labs(title = "Model 3")
draw_scatterplots(model4, params = params) + labs(title = "Model 4")
```

@@

```{r fig.height=8}
draw_ksplots_D(model1) + labs(title = "Model 1")
draw_ksplots_D(model2) + labs(title = "Model 2")
draw_ksplots_D(model3) + labs(title = "Model 3")
draw_ksplots_D(model4) + labs(title = "Model 4")
```

@@

```{r fig.height=8}
# draw_ksplots_l(model1) + labs(title = "Model 1")
# draw_ksplots_l(model2) + labs(title = "Model 2")
# draw_ksplots_l(model3) + labs(title = "Model 3")
# draw_ksplots_l(model4) + labs(title = "Model 4")
```

@@

```{r}
map(model1, "mcmc_traceplots")
map(model2, "mcmc_traceplots")
map(model3, "mcmc_traceplots")
map(model4, "mcmc_traceplots")
```

@@

```{r}
draw_rhatplot(model1) + labs(title = "Model 1")
draw_rhatplot(model2) + labs(title = "Model 2")
draw_rhatplot(model3) + labs(title = "Model 3")
draw_rhatplot(model4) + labs(title = "Model 4")
```
